RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Equations
Not necessarily the CDF

\subsection{Proposals that modify objects}

>>>>

\subsection{Proposals that modify objects}
We now consider a proposal distribution that modifies one or more of the
objects $\{x_i\}$, while keeping the number of objects $N$, as well as the
hyperparameters $\alpha$, fixed.

Let $F(x; \alpha)$ be a function that takes an object $x$ and transforms it
to a value $u$ that has a uniform distribution between 0 and 1, given $\alpha$.
If the object $x$ consists of a single scalar value, $F$ is the cumulative
distribution of the interim prior. Denote the inverse of $F$ by $G$.

A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F$,
making the proposal in terms of $u$, and then transforming back.
Specifically, the proposal chooses
a new value $x_i'$ from the current value $x_i$ as follows:
\begin{eqnarray}
u_i &=& F(x_i; \alpha)\\
u_i' &=& \textnormal{mod}\left(u_i + \delta_u, 1\right)\\
x_i' &=& F^{-1}(u_i'; \alpha).
\end{eqnarray}
